% adding the line below for Multifile document support with LatexTools Sublime package 
%!TEX root = manuscript.tex

% conclusion

\section{Conclusion}

This work confirms \citet{Cortese2016}'s findings in the light of recently published clinical works.
In particular, studies following a standard protocol as defined by \citet{Arns2014} show significant 
clinical improvements on \gls{pblind} raters (k = 4 studies instead of 3 \citet{Cortese2016}).

Besides a meta-analysis, a new method is suggested here to tackle the high heterogeneity of clinical data 
available on \gls{nfb}. This method aims at identifying factors that are positively or negatively contributing 
to \gls{nfb} efficacy. Three factors were consistently found to explain clinical 
within-\gls{es}. First, the quality of acquisition of the \gls{eeg} was positively correlated with clinical 
efficacy. This supports a mode of action through specific \gls{eeg} training. Likewise, treatment intensity was 
found to contribute, corroborating what is known from learning theory (memory consolidation) \citep{Mowrer1960}, 
that is, a more intense treatment leads to an increased clinical efficacy. Finally, results show that the therapeutic 
efficacy measured by teachers is reduced compared to that measured by parents. This result has long been documented 
and it is widely advanced that this difference is solely imputable to the amplitude of placebo effect in \gls{nfb}. 
However, the data presented in this article, in line with the most recent work on the topic \citep{Sollie2013, Narad2015, Minder2018} 
tend to refute this hypothesis and suggests instead that teachers are simply less likely to be exposed to symptoms. 
As a consequence, using \gls{pblind} endpoints to address the specificity of the clinical efficacy is not recommended 
and we advice instead to rely on other available methodological tools. Those include sham \gls{nfb} and neuromarker 
analysis investigating the specificity of the \gls{eeg} changes with respect to trained neuromarkers as well as changes 
in clinical endpoints.

These elements converge to the conclusion that existing methodologies, in particular the double blind design, 
traditionally used to assess pharmacological treatments 
in neuropsychiatric conditions may not be fully fitted to the evaluation of medical devices. The series of results presented 
here, however, suggest the presence of a genuine signal in favor of the therapeutic efficacy of \gls{nfb}. A signal that 
should nonetheless be studied further using the aforementioned methodological tools, neuromarker analysis in the first place.

This work also offers an open-source toolbox for running meta-analysis and \gls{saob}: the code and data used are available 
assuring the transparency and replicability of these analysis, as well as fostering future ones. 

% 375
